Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-11 article/article.tex
results

Table~\ref{tab:results} illustrates the overall performance of the three classifiers. Rows indicate various feature selection methods. We applied PCA to the original data, while the rest feature selection methods were applied to the data belonging to the selected ROIs (cf.~Section~\ref{sec:dimensionalityReduction}). For instance, \emph{Norm/Vox-M-SD ROIs} indicates that we normalised over the voxel values of the same voxel index using the mean and standard deviation, while \emph{Norm-M-SD ROIs} indicates that we normalised over the voxel values of the same scan index using the mean and standard deviation. Columns depict the used classifiers. For the classifiers depicted with *, we used a different method for structuring the data, as described in Section~\ref{sec:trainingMethodsAndClassifiers}.

Furthermore, to test the significance of the differences in performance between the different methods we performed an exact binomial test in each case, from which we obtained the confidence interval. The results were rounded to one decimal point. For the rest of this section and to explain some of the results we are looking only at the case when \emph{Norm/Vox-M-SD ROIs} is used as a feature selection method.

>>>>

Table~\ref{tab:results} illustrates the overall performance of the three classifiers. Rows indicate various feature selection methods. We applied PCA to the original data, while the rest feature selection methods were applied to the data belonging to the selected ROIs (cf.~Section~\ref{sec:dimensionalityReduction}). For instance, \emph{Norm/Vox-M ROIs} indicates that we normalised over the voxel values of the same voxel index using only the mean, while \emph{Norm-M-SD ROIs} indicates that we normalised over the voxel values of the same scan index using the mean and standard deviation. Columns depict the used classifiers. For the classifiers depicted with *, we used a different method for structuring the data as described in Section~\ref{sec:trainingMethodsAndClassifiers}.

Furthermore, to test the significance of the differences in performance between the different methods we performed an exact binomial test in each case, from which we obtained the confidence interval. The results were rounded to one decimal point. For the rest of this section and to explain some of the results we are looking only at the case when \emph{Norm/Vox-M ROIs} is used as a feature selection method.
